\chapter{Introduction}

\section{What is Prior RTOS?}

Prior RTOS is an embedded Real-Time Operating System with a small footprint and high customizability enabling it to run smoothly on even the smallest devices such as Atmel’s ATMega series. This combined with the fact that the kernel is entirely written in C99 makes it portable to almost any microcontroller or microprocessor architecture. With Prior RTOS the development of event driven real-time applications becomes a painless process using the wide variety of intuitive API functions.

\section{Core values}

\textbf{Adaptability}

\textbf{Security and Isolation}


\section{Features}
\begin{pditemize}
\item Cooperative scheduler based on weighted FIFO.
\item Priority system with 4 categories to indicate scheduling/timing constraints and a priority level ranging from 1 through 5.
\item Software Timer module with possible sub-millisecond intervals.
\item Inter-Task Communication (ITC) system providing eventgroups, mailboxes, semaphores/mutexes and ringbuffers.
\item Global Events allowing tasks to Wait and Poll for all possible events.
\item Advanced Memory Management giving the programmer protected memory pools allowing dynamic allocations on the statically allocated OS heap.
\item Low OS Tick overhead: ~750 clock-cycles (on AVR8).
\item Small footprint kernel with a minimal size of 15 kB ROM and 350 Bytes of RAM (O0).
\item Configurable memory usage, modules, peripherals and utilities to tailor the OS to your application.
\end{pditemize}
