\section{\textit{Eventgroup} API}

\subsection{EventgroupCreate}
\label{func:EventgroupCreate}
\begin{pdfunction}
{EventgroupCreate(void) }
{ 
Creates a new eventgroup. Each eventgroup register contains 
flags that can individually set or cleared. }
\pdfunctionreturn{(Id_t) }{Eventgroup ID }{INVALID_ID}{if an error occurred during creation. }
\pdfunctionreturn{(Id_t) }{Eventgroup ID }{Other}{if the eventgroup was successfully created. }
\end{pdfunction}

\subsection{EventgroupDelete}
\label{func:EventgroupDelete}
\begin{pdfunction}
{EventgroupDelete(Id\_t evengroup\_id) }
{ 
Deletes an existing eventgroup. The evengroup\_id will be set 
INVALID\_ID if the operation is successful. }
\pdfunctionargin{(Id_t *) eventgroup_id}{ Eventgroup ID. }
\pdfunctionreturn{(OsResult_t) }{sys call result }{OS_OK}{if the eventgroup was successfully deleted. }
\pdfunctionreturn{(OsResult_t) }{sys call result }{OS_ERROR}{if the eventgroup could not be found. }
\end{pdfunction}

\subsection{EventgroupFlagsSet}
\label{func:EventgroupFlagsSet}
\begin{pdfunction}
{void EventgroupFlagsSet(Id\_t eventgroup\_id, U8\_t mask) }
{ 
Sets the masked flags in the eventgroup register. 
if mask = (EVENTGROUP\_FLAG\_MASK\_3 |EVENTGROUP\_FLAG\_MASK\_7), 
3 and 7 will be set. }
\pdfunctionargin{(Id_t) eventgroup_id}{ Eventgroup ID. }
\pdfunctionargin{(U8_t) mask}{ Event flag mask. }
\pdfunctionreturn{(OsResult_t) }{sys call result }{OS_OK}{if the eventgroup was successfully deleted. }
\pdfunctionreturn{(OsResult_t) }{sys call result }{OS_ERROR}{if the eventgroup could not be found. }
\end{pdfunction}

\subsection{EventgroupFlagsClear}
\label{func:EventgroupFlagsClear}
\begin{pdfunction}
{EventgroupFlagsClear(Id\_t evengroup\_id, U8\_t mask) }
{ 
Clears the masked flags in the eventgroup register. 
if mask = (EVENTGROUP\_FLAG\_MASK\_0 |EVENTGROUP\_FLAG\_MASK\_4), 
0 and 4 will be cleared. }
\pdfunctionargin{(Id_t) eventgroup_id}{ Eventgroup ID. }
\pdfunctionargin{(U8_t) mask}{ Event flag mask. }
\pdfunctionreturn{(OsResult_t) }{sys call result }{OS_OK}{if the eventgroup was successfully deleted. }
\pdfunctionreturn{(OsResult_t) }{sys call result }{OS_ERROR}{if the eventgroup could not be found. }
\end{pdfunction}

\subsection{EventgroupFlagsGet}
\label{func:EventgroupFlagsGet}
\begin{pdfunction}
{EventgroupFlagsGet(Id\_t evengroup\_id, U8\_t mask) }
{ 
Returns the eventgroup flags specified in the mask. }
\pdfunctionargin{(Id_t) eventgroup_id}{ Eventgroup ID. }
\pdfunctionargin{(U8_t) mask}{ Event flag mask. }
\pdfunctionreturn{(U8_t) }{Eventgroup flags. }{}{}
\end{pdfunction}
