\section{\textit{Timer} API}

\subsection{TimerCreate}
\label{func:TimerCreate}
\begin{pdfunction}
{TimerCreate(U32\_t interval, U8\_t parameter) }
{ 
Creates a timer that will overflow after the specified 
If the TIMER\_PARAMETER\_ON flag is set, the timer will start 
creation. The number of iterations before auto-delete can be 
through the use of the parameter. 
overflowing the timer will do the following: 
Always: Generate an overflow event. 
If TIMER\_PARAMETER\_ON = 1: Start the timer. 
If TIMER\_PARAMETER\_AR = 1: Automatically reset. 
If TIMER\_PARAMETER\_P = 0: Decrement the number of iterations left. 
If iterations left = 0: Delete the timer. 
parameter macros 
(auto-reset) 
(on) 
TIMER\_PARAMETER\_P(periodic)
(sets iterations for parameter) 
(gets iterations from parameter) }
\pdfunctionargin{(U32_t) interval_us}{ Timer interval in microseconds(us), 0xFFFFFFFF is illegal. }
\pdfunctionargin{(U8_t) parameter}{ Timer parameter. }
\pdfunctionreturn{(Id_t) }{Timer ID }{INVALID_ID}{if creation failed. }
\pdfunctionreturn{(Id_t) }{Timer ID }{Other}{if the timer was created. }
\end{pdfunction}

\subsection{TimerDelete}
\label{func:TimerDelete}
\begin{pdfunction}
{TimerDelete(Id\_t timer\_id) }
{ 
Deletes the specified timer and sets timer\_id to INVALID\_ID if the 
is successful. }
\pdfunctionreturn{(OsResult_t) }{sys call result }{OS_OK}{if the timer was successfully deleted. }
\pdfunctionreturn{(OsResult_t) }{sys call result }{OS_ERROR}{if the timer could not be found. }
\end{pdfunction}

\subsection{TimerStop}
\label{func:TimerStop}
\begin{pdfunction}
{TimerStop(Id\_t timer\_id) }
{ 
Stops the specified timer, it will not start unless TimerStart 
called. The timer is transitioned to the stopped-state. 
current ticks on the timer are REMOVED, to save the ticks use TimerPause. }
\pdfunctionargin{(Id_t) timer_id}{ ID of the timer to stop. }
\pdfunctionreturn{(OsResult_t) }{sys call result }{OS_OK}{if the timer was successfully stopped. }
\pdfunctionreturn{(OsResult_t) }{sys call result }{OS_ERROR}{if the timer could not be found. }
\end{pdfunction}

\subsection{TimerStart}
\label{func:TimerStart}
\begin{pdfunction}
{TimerStart(Id\_t timer\_id) }
{ 
Starts the specified timer. }
\pdfunctionargin{(Id_t) timer_id}{ ID of the timer to start. }
\pdfunctionreturn{(OsResult_t) }{sys call result }{OS_OK}{if the timer was successfully started. }
\pdfunctionreturn{(OsResult_t) }{sys call result }{OS_ERROR}{if the timer could not be found. }
\end{pdfunction}

\subsection{TimerPause}
\label{func:TimerPause}
\begin{pdfunction}
{TimerPause(Id\_t timer\_id) }
{ 
Pauses the specified timer, it will not start unless TimerStart 
called. The timer is transitioned to the stopped-state. 
current ticks on the timer are SAVED, to remove ticks use TimerStop or 
TimerReset.}
\pdfunctionargin{(Id_t) timer_id}{ ID of the timer to pause. }
\pdfunctionreturn{(OsResult_t) }{sys call result }{OS_OK}{if the timer was successfully paused. }
\pdfunctionreturn{(OsResult_t) }{sys call result }{OS_ERROR}{if the timer could not be found. }
\end{pdfunction}

\subsection{TimerReset}
\label{func:TimerReset}
\begin{pdfunction}
{TimerReset(Id\_t timer\_id) }
{ 
Resets the timer's current ticks and transitions it to the 
state. }
\pdfunctionargin{(Id_t) timer_id}{ ID of the timer to reset. }
\pdfunctionreturn{(OsResult_t) }{sys call result }{OS_OK}{if the timer was successfully reset. }
\pdfunctionreturn{(OsResult_t) }{sys call result }{OS_ERROR}{if the timer could not be found. }
\end{pdfunction}

\subsection{TimerStartAll}
\label{func:TimerStartAll}
\begin{pdfunction}
{TimerStartAll(void) }
{ 
Starts all timers that exist at the time of the call. }
\end{pdfunction}

\subsection{TimerStopAll}
\label{func:TimerStopAll}
\begin{pdfunction}
{TimerStopAll(void) }
{ 
Stops all timers that exist at the time of the call. }
\end{pdfunction}

\subsection{TimerResetAll}
\label{func:TimerResetAll}
\begin{pdfunction}
{TimerResetAll(void) }
{ 
Reset all timers that exist at the time of the call. }
\end{pdfunction}

\subsection{}
\label{func:}
\begin{pdfunction}
{TimerGetState (Id\_t timer\_id) }
{ 
Returns the current state of the timer. }
\pdfunctionargin{(Id_t) timer_id}{ Timer ID. }
\pdfunctionreturn{(TmrState_t) }{current state }{TIMER_STATE_STOPPED}{}
\pdfunctionreturn{(TmrState_t) }{current state }{TIMER_STATE_WAITING}{}
\pdfunctionreturn{(TmrState_t) }{current state }{TIMER_STATE_RUNNING}{}
\pdfunctionreturn{(TmrState_t) }{current state }{TIMER_STATE_INVALID}{if the timer could not be found. }
\end{pdfunction}

\subsection{}
\label{func:}
\begin{pdfunction}
{TimerTicksGet (Id\_t timer\_id) }
{ 
Returns the current value of the timer's counter. }
\pdfunctionargin{(Id_t) timer_id}{ Timer ID. }
\pdfunctionreturn{(U32_t) }{counter value }{TIMER_INTERVAL_ILLEGAL}{if the timer could not be found. }
\pdfunctionreturn{(U32_t) }{counter value }{Other}{valid counter value. }
\end{pdfunction}

\subsection{TimerIntervalSet}
\label{func:TimerIntervalSet}
\begin{pdfunction}
{TimerIntervalSet(Id\_t timer\_id, U32\_t new\_interval\_us) }
{ 
Sets a new interval for the timer. The timer is NOT implicitly 
reset.}
\pdfunctionargin{(Id_t) timer_id}{ Timer ID. }
\pdfunctionargin{(U32_t) new_interval_us}{ New Timer interval in microseconds(us), }
\end{pdfunction}

\subsection{}
\label{func:}
\begin{pdfunction}
{TimerIntervalGet (Id\_t timer\_id) }
{ 
Returns the current interval of the timer in us. }
\pdfunctionargin{(Id_t) timer_id}{ Timer ID. }
\pdfunctionreturn{(U32_t) }{timer interval }{TIMER_INTERVAL_ILLEGAL}{if the timer could not be found. }
\pdfunctionreturn{(U32_t) }{timer interval }{Other}{valid interval. }
\end{pdfunction}

\subsection{TimerIterationsGet}
\label{func:TimerIterationsGet}
\begin{pdfunction}
{TimerIterationsGet(Id\_t timer\_id) }
{ 
Returns the current amount of iterations left on the timer. }
\pdfunctionargin{(Id_t) timer_id}{ Timer ID. }
\pdfunctionreturn{(U8_t) }{timer iterations }{0}{if the timer could not be found. }
\pdfunctionreturn{(U8_t) }{timer iterations }{131}{for a valid number of iterations. }
\end{pdfunction}

\subsection{TimerIterationsSet}
\label{func:TimerIterationsSet}
\begin{pdfunction}
{TimerIterationsSet(Id\_t timer\_id, U8\_t iterations) }
{ 
Sets the amount of iterations left on the timer. The value 
be between 1 and 31. }
\pdfunctionargin{(Id_t) timer_id}{ Timer ID. }
\pdfunctionargin{(U8_t) iterations}{ Number of iterations, 1-31. }
\pdfunctionreturn{(OsResult_t) }{Sys call result: }{OS_OK}{if the operation was successful. }
\pdfunctionreturn{(OsResult_t) }{Sys call result: }{OS_ERROR}{if the timer could not be found. }
\pdfunctionreturn{(OsResult_t) }{Sys call result: }{OS_OUT_OF_BOUNDS}{if the iteration value was > 31 or 0. }
\end{pdfunction}

\subsection{}
\label{func:}
\begin{pdfunction}
{TimerParameterGet (Id\_t timer\_id) }
{ 
Returns the current parameter of the timer. 
parameter bits | 7-3: iterations | 2: auto-reset | 1: periodic | 0: ON | 
Arguments:}
\pdfunctionargin{(Id_t) timer_id}{ Timer ID. }
\pdfunctionreturn{(U8_t) }{Sys call result: }{0xFF}{if the timer could not be found. }
\pdfunctionreturn{(U8_t) }{Sys call result: }{Other}{valid parameter. }
\end{pdfunction}

\subsection{}
\label{func:}
\begin{pdfunction}
{TimerParameterSet (Id\_t timer\_id) }
{ 
Sets a new parameter for the timer. 
parameter bits | 7-3: iterations | 2: auto-reset | 1: periodic | 0: ON | 
Arguments:}
\pdfunctionargin{(Id_t) timer_id}{ Timer ID. }
\pdfunctionargin{(U8_t) parameter}{ New timer parameter. 0xFF is illegal. }
\end{pdfunction}
